%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  %---------------------------------------------------------
  \cventry
    {Senior iOS Engineer} % Job title
    {Pictet-Technologies} % Organization
    {Esch-sur-Alzette, Luxembourg} % Location
    {Oct. 2023 - PRESENT} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Pioneered iOS development as the first iOS engineer, establishing best practices and mentoring colleagues on Swift development and iOS architecture patterns.}
      \item {Led refactoring initiatives for banking application transitioning from white label to custom solution, introducing MVVM-C architecture, dependency injection, and modular design patterns.}
      \item {Implemented comprehensive testing strategy including unit tests, UI tests, and snapshot tests to ensure code quality and maintainability, reducing tester overload by automating regression testing.}
      \item {Developed automated tests using XCUITest that covered 90\% of the regression tests done by the QA, reducing manual testing effort and accelerating release cycles.}
      \item {Automated the integration of new translations, enabling faster localization and consistent rollout across supported languages.}
    \end{cvitems}
    }
  %---------------------------------------------------------
  \cventry
    {Senior iOS Engineer} % Job title
    {Growin: Celfocus \& Vodafone} % Organization
    {Lisbon, Portugal} % Location
    {Oct. 2022 - Sep. 2023} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed and enhanced features for Vodafone Smart App serving serveral users, focusing on CallKit, PushKit, SwiftUI, UIKit, ReactiveSwift, and CoreBluetooth integration.}
      \item {Led integration of Firebase Tools and Sourcery into the development stack to streamline analytics and code generation workflows.}
      \item {Collaborated with cross-functional teams to deliver app features and SDK updates, maintaining high stakeholder satisfaction and on-time delivery.}
    \end{cvitems}
    }

  %---------------------------------------------------------
  \cventry
      {Mobile Engineer} % Job title
      {DSR Corporation} % Organization
      {Porto, Portugal} % Location
      {Feb. 2022 - Sep. 2022} % Date(s)
      {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built digital cash wallet app using React-Native, improving user financial accessibility.}
        \item {Implemented iOS native features in Swift, seamlessly integrating with React-Native stack to enhance app performance and user experience.}
        \item {Integrated Hyperledger Aries and DidComm for secure communication and decentralized identity support, ensuring high security standards.}
      \end{cvitems}
      }

  %---------------------------------------------------------
  \cventry
      {Mobile Software Engineer I} % Job title
      {Agi - Bank Institution} % Organization
      {Porto Alegre, Brazil} % Location
      {Jun. 2021 - Jan. 2022} % Date(s)
      {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and maintained payment features in Agibank's mobile app using Swift and SwiftUI.}
        \item {Implemented new screen flows, API integrations, and comprehensive testing strategies.}
        \item {Resolved critical bugs and performance issues, ensuring high app stability and user satisfaction.}
      \end{cvitems}
      }

  % %---------------------------------------------------------
  % \cventry
  %     {Mobile Software Engineer} % Job title
  %     {Fraunhofer IESE} % Organization
  %     {Kaiserslautern, Germany} % Location
  %     {Mar. 2020 - Feb. 2021} % Date(s)
  %     {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Developed client-side applications in C\# using Xamarin.Forms, delivering cross-platform functionality.}
  %       \item {Conducted QA sessions and stress tests to ensure software performance and reliability.}
  %       \item {Designed new screen flows, investigated issues, and resolved critical bugs.}
  %       \item {Streamlined development using tools like Git, Jenkins, Jira, and Confluence.}
  %     \end{cvitems}
  %   }

  %---------------------------------------------------------
  \cventry
    {iOS Developer} % Job title
    {Apple Developer Academy PUCRS} % Organization
    {Porto Alegre, Brazil} % Location
    {Feb. 2015 - Dec. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed iOS, tvOS, and watchOS applications in Swift and Objective-C.}
        \item {Managed projects using Scrum and Agile methodologies, ensuring timely delivery.}
        \item {Performed unit testing to maintain high-quality, reliable code.}
      \end{cvitems}
    }

%-------------------------------------------------------------------------------
\end{cventries}
